Evaluating machine translation for assimilation via a gap-filling task

### 2015-02-28 2015-eamt-assim/2015-eamt-assim.tex
Added Krippendorff reference
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@59164 72bbbca6-d526-0410-a7d9-f06f51895060

\subsection{Annotator agreement}
After obtaining the results we calculated Krippendorff's alpha measure to represent annotator agreement, shown in Tables~\ref{table:alpha-eus-spa} and~\ref{table:alpha-tat-rus}. We selected this measure because of its compatibility with more than two annotators per task and the missing data (not all the gaps were evaluated). To calculate Krippendorff's alpha we used an algorithm implementation by Thomas Grill\footnote{http://grrrr.org}, dividing the answers in each gap into two categories: correct and incorrect. The previously obtained synonym lists were taken into account, i.e. if the two answers are different but both correct, they fall into one category. The measure was calculated separately for each hint and percentage combination.

>>>>

\subsection{Annotator agreement}
After obtaining the results we calculated Krippendorff's alpha~\citep{krippendorff70} measure to represent annotator agreement, shown in Tables~\ref{table:alpha-eus-spa} and~\ref{table:alpha-tat-rus}. We selected this measure because of its compatibility with more than two annotators per task and the missing data (not all the gaps were evaluated). To calculate Krippendorff's alpha we used an algorithm implementation by Thomas Grill\footnote{http://grrrr.org}, dividing the answers in each gap into two categories: correct and incorrect. The previously obtained synonym lists were taken into account, i.e. if the two answers are different but both correct, they fall into one category. The measure was calculated separately for each hint and percentage combination.
